Retrofitting Effect Handlers onto OCaml

### 2020-11-02 retro-concurrency.tex
Added skeleton of what to present in the evaluation section

>>>>

\subsection{The impact on code not using effects}

There are several changes to the runtime to support fibers and effect handlers
that will be executed by code not using effects: OCaml stacks now have dynamic
checks in the function prologue and the FFI interface tracks stack switching.

TODO:
\begin{itemize}
\item Aim: |R1| not altered existing code performance too much
\item sandmark macro benchmarks to show sequential performance: 4.10.0+stock, 4.10.0+multicore,
4.10.0+multicore no red-zone/leaf-optimization, 4.10.0+multicore
\item do we want to include some micro-benchmarks focusing on the FFI callstack overhead?
\end{itemize}

\subsection{Measurements of overheads in our effects implementation}

We have implemented effects within OCaml, here we present timing measurements
for the various stages of stack creation (|a| to |b|), performing and handling
an effect (|b| to |c|), continuation resumption (|c| to |d|) and returning from
a computation and freeing the stack (|d| to |e|).

\begin{lstlisting}
let foo () =
 (* a *) match
 (* b *)   perform E
 (* d *) with effect E k ->
 (* c *)   continue k ()
 (* e *)
\end{lstlisting}

TODO:
\begin{itemize}
\item Aim: |R3| to provide some timing information as to the size of the overhead and where the overhead is.
\item use KC's measurement stubs as presented in WASM
\end{itemize}

\subsection{Effects benchmarks}

We now look at the impact of the overhead in a variety of benchmarks comparing
the cost of using our effects abstraction versus alternative methods of
implementation.

TODO:
\begin{itemize}
\item Aim: |R3| Do we have an efficient implementation of effects and are effects competitive vs alternative implementation strategies.
\item we can show the sequential vs stack benchmarks as used by 'Folklore to fact' \tk{slightly weak story as the sequential ones will be much faster for these very simple benchmarks and effects don't really add anything to their implementation}
\item general generator examples (using examples from effects-example)
\item chamenos vs chamenos effects vs lwt (using examples from effects-example)
\end{itemize}

\subsection{Webserver benchmarks}

TODO:
\begin{itemize}
\item Aim: |R3| Do we have an efficient implementation of effects.
\item effects are a very nice way to program non-blocking IO for webservers
\item show that using effects doesn't impose undue overhead and that we are competitive with LWT, Async, Go with the wrk web benchmark
\end{itemize}

\subsection{Using fibers for task based parallelism}

TODO:
\begin{itemize}
\item Aim: |R3| Do we have an efficient implementation of effects.
\item minor alteration to domainslib to launch tasks in their own stack
\item effects are the right way to do some task base parallelism. Use the nqueens example and show the scaling we can achieve in parallel
\item show that using fibers doesn't have large detrimental impact to existing parallel applications: Take sandmark: minilight, nbody, LU decomposition
\end{itemize}
